---
title: "Game of Thrones Analysis"
output: pdf_document
params:
  season_num: 1
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Game of Thrones - Season `r params$season_num`

 
```{r ,include=FALSE}

load(paste0("C:/Users/rafal/Downloads/Studia_II_rok/Drugi_semestr/Reproducible_research/GIT_PULL_RR_repo/Data/season_", params$season_num, ".RData"))
```
(Warning: spoilers ahead)
Overview

(From the Wikipedia) Game of Thrones is an American fantasy drama television series created by David Benioff and D. B. Weiss for HBO. It is an adaptation of A Song of Ice and Fire, a series of fantasy novels by George R. R. Martin, the first of which is A Game of Thrones.

Set on the fictional continents of Westeros and Essos, Game of Thrones has a large ensemble cast and follows several story arcs throughout the course of the show. A major arc concerns the Iron Throne of the Seven Kingdoms of Westeros through a web of political conflicts among the noble families either vying to claim the throne or fighting for independence from it. Another focuses on the last descendant of the realm's deposed ruling dynasty, who has been exiled to Essos and is plotting a return to the throne. A third story arc follows the Night's Watch, a military order defending the realm against threats from the North.

```{r, include=FALSE}

# calculate the average viewership
avg_viewership <- mean(season_data$viewers)

# filter the episodes with above-average viewership
above_avg_episodes <- season_data[season_data$viewers > avg_viewership, ]
```
You can see how the viewership of the episodes changed in Figure 1.

```{r, include=FALSE}

plot(season_data$viewers, type="l", col="red", lwd=5, xlab = "Episode number", ylab = "1st day TV viewers in the US (millions)")
```

Finally, the episodes with the above-average viewership were:

```{r}

library(knitr)
kable(above_avg_episodes[,c("no_overall", "title", "directed_by")], col.names = c("no_season", "title", "directed_by"), align = 'c')
```



