---
title: "GoT Season Report"
author: "Daniel Śliwiński"
date: '`r Sys.Date()`'
output: html
---

```{r include=FALSE}
library(quarto)

for (i in 1:8) {
  quarto_render(
    "qmd_homework_3.qmd", 
    output_format = "html",
    output_file = paste0("report_season_", i, ".html"),
    execute_params = list(season_number = i)
  )
}
```

```{r include=FALSE}
season_data <- read.csv(paste0("../Data/season_", params$season_number, ".csv"))
library(knitr)
library(ggplot2)
library(dplyr)
library(lubridate)
library(stringr)
Sys.setlocale("LC_TIME", "en_US")

episodes_num <- nrow(season_data)

first_date <- season_data %>%
  arrange(no_season) %>%
  slice(1) %>%
  pull(premiere_date)

last_date <- season_data %>%
  arrange(no_season) %>%
  tail(1) %>%
  pull(premiere_date)

# Remove the part of the date string in parentheses

first_date_cleaned <- substr(first_date, start = 1, stop = 14)
last_date_cleaned <- substr(last_date, start = 1, stop = 14)

# Convert the cleaned date strings to Date objects
first_date_parsed <- lubridate::mdy(first_date_cleaned)
last_date_parsed <- lubridate::mdy(last_date_cleaned)

# Extract month, day, and year
month1 <-month.name[month(first_date_parsed)]
day1 <- day(first_date_parsed)
year1 <- year(first_date_parsed)

month2 <- month.name[month(last_date_parsed)]
day2 <- day(last_date_parsed)
year2 <- year(last_date_parsed)

avg_views <- season_data %>% pull(viewers) %>% mean()

most_popular_episode <- season_data %>%
  filter(viewers == max(viewers)) %>%
  select(title, description)
```

***

### Season `r params$season_number` summary

Season `r params$season_number` of Game of Thrones consisted of `r episodes_num` episodes that aired between `r month1` `r day1` and `r month2` `r day2`, `r year2` on HBO. The show gathered an average of `r avg_views` first-day TV viewers in the US.

The most popular episode of the season was `r most_popular_episode$title`, in which:

> "`r most_popular_episode$description`"

***

You can see how the viewership of the episodes changed in Figure 1.

```{r name=paste0("views_per_episode_", params$season_number), echo=FALSE, fig.cap="First day views from episode to episode"}
plot(season_data$viewers,
     type="l", col="red", lwd=5,
     xlab = "Episode number",
     ylab = "1st day TV viewers in the US (millions)")

```
***

Finally, the episodes with the above-average viewership were:

```{r echo=FALSE, results='asis'}
top_episodes <- season_data[order(-season_data$viewers), ][1:4, ]
top_episodes <- top_episodes %>% select(no_season, title, directed_by, written_by, premiere_date)
knitr::kable(top_episodes, col.names = c("No. in Season", "Title", "Directed by", "Written by", "Premiere Date"))

```
***
