---
title: "Metaanalysis in R"
author: "Muhammad SAqib Masood"
date: today
format:  
  html:
    theme: lumen
    toc: true
    toc_float: true
title-block-banner: true
execute:
  echo: fenced
---

```{r}
#| label = "setup",
#| include = FALSE
library(meta)
library(metafor)
library(dplyr)
#setwd("")
```

```{r}
install.packages("meta")
```

## Metaanalysis

*a statistical analysis that combines the results of multiple scientific studies.* ([Wikipedia](https://en.wikipedia.org/wiki/Meta-analysis))

Very important in e.g. medicine (where it's relatively easy to use).

Can serve different goals:

1) Finding the "true" size of the relationship based on multiple studies.
2) Finding the average effect size based on multiple studies.
3) Finding what affects the relationship:
  - study-related (e.g. author effects, journal effects, method effects, variable selection, etc.)
  - context-related (e.g. changes over time, sample characteristics, country, etc.)
4) Uncovering publication biases (e.g. a meta-analysis of several studies with statistically significant results may conclude that there is not enough evidence)

```{r}
library(readxl)
data <- read_excel("C:\\Users\\HP\\Desktop\\Study\\semester_4\\ReproducibleResearch\\RRcourse2023\\13. Metaanalysis\\metaanalysis_data.xlsx")

```
## Case 1: Fixed Effects

```{r}
fixed <- meta::metagen(TE=Mean_boys_play_male,
             seTE=SD_boys_play_male,
             data=data,
             studlab=paste(Study),
             comb.fixed = TRUE,
             comb.random = FALSE)

fixed
```

## Case 2: Combining both Fixed and Random Effects

```{r}
fixed_Random <- meta::metacont(n.e=N_boys,
                  mean.e=Mean_boys_play_male,
                  sd.e=SD_boys_play_male,
                  n.c=N_boys,
                  mean.c=Mean_girls_play_male,
                  sd.c=SD_girls_play_male,
                  data=data,
                  studlab=paste(Study),
                  comb.fixed = TRUE,
                  comb.random = TRUE,
)
fixed_Random
```

## Case 3: Random Effect

```{r}
randomEffect <- meta::metagen(TE=Mean_boys_play_male,
             seTE=SD_boys_play_male,
             data=data,
             studlab=paste(Study),
             comb.fixed = FALSE,
             comb.random = TRUE)
randomEffect
```

```{r}
fixed %>% forest(sortvar=Mean_boys_play_male)
```



```{r}
fixed %>% metareg(~ `Female authors` + `Male authors`)
  
```  


## Creating Funnel Plot


```{r}
randomEffect %>% funnel()
```

The above plot shows asymmetry or clustering of data points, it might indicate the presence of publication bias or heterogeneity.


```{r}
contour_levels <- c(0.70, 0.75, 0.75)
contour_colors <- c("yellow", "green", "red")
funnel(randomEffect, contour = contour_levels, col.contour = contour_colors)
legend("topright", c("p < 0.10", "p < 0.05", "p < 0.01"), bty = "n", fill = contour_colors)
```

