---
title: "Metaanalysis example  in R"
author: "Temmuz Yavuzer 444130"
date: today
format:  
  html:
    theme: lumen
    toc: true
    toc_float: true
title-block-banner: true
execute:
  echo: fenced
---

```{r}
#| label = "setup",
#| include = FALSE
library(meta)
library(metafor)
library(dplyr)
```
## Metaanalysis assignment of RR 

*Assignment.* 


-  combine the effects for female

-  create a funnel plot for female (what do you see?)

-  check if methods / quality affect the results

-  does author gender affect it?

---

```{r}
library(readxl)
data <- read_excel("C:/Users/Lanzelit/Documents/GitHub/RRcourse2023/13. Metaanalysis/data/metaanalysis_data.xlsx")
View(data)
```

# Fixed Effect
```{r}
FE <- meta::metagen(TE=Mean_girls_play_female,
             seTE=SD_girls_play_female,
             data=data,
             studlab=paste(Study),
             comb.fixed = TRUE,
             comb.random = FALSE)

FE
```

# Meta-analysis on the effect of gender

```{r}
meta_girls <- meta::metacont(n.e=N_girls,
                  mean.e=Mean_girls_play_female,
                  sd.e=SD_girls_play_female,
                  n.c=N_boys,
                  mean.c=Mean_girls_play_male,
                  sd.c=SD_girls_play_male,
                  data=data,
                  studlab=paste(Study),
                  comb.fixed = TRUE,
                  comb.random = TRUE,
)
meta_girls
```
# Random Effects 
```{r}
RE <- meta::metagen(TE=Mean_girls_play_female,
             seTE=SD_girls_play_female,
             data=data,
             studlab=paste(Study),
             comb.fixed = FALSE,
             comb.random = TRUE)
RE
```

# Forest plot 
```{r}
FE %>% forest(sortvar=Mean_girls_play_female)
```



# How does gender affect it?

```{r}
FE %>% metareg(~ `Female authors` + `Male authors`)
  
```  
-  The intercept represents the estimated effect when the moderator variables are zero. In this case, the estimated intercept is 151.2803, indicating the baseline effect.
-  The coefficient for Female authors is -7.9308 with a standard error of 20.8577 and a p-value of 0.7038, suggesting - that the presence of female authors does not have a significant effect on the outcome.
-  The coefficient for Male authors is -17.7918 with a standard error of 23.1683 and a p-value of 0.4425, indicating that the presence of male authors also does not have a significant effect on the outcome.

## Funnel Plot


```{r}
RE %>% funnel()
```


```{r}
contour_levels <- c(0.90, 0.95, 0.99)
contour_colors <- c("darkblue", "blue", "lightblue")
funnel(RE, contour = contour_levels, col.contour = contour_colors)
legend("topright", c("p < 0.10", "p < 0.05", "p < 0.01"), bty = "n", fill = contour_colors)
```

