---
title: "Metaanalysis in R"
author: "Syed Ahmad Jamal"
date: today
format:  
  html:
    theme: lumen
    toc: true
    toc_float: true
title-block-banner: true
execute:
  echo: fenced
---

```{r}
#| label = "setup",
#| include = FALSE
library(meta)
library(metafor)
library(dplyr)
#setwd("")
```

## Metaanalysis

*a statistical analysis that combines the results of multiple scientific studies.* ([Wikipedia](https://en.wikipedia.org/wiki/Meta-analysis))

Very important in e.g. medicine (where it's relatively easy to use).

Can serve different goals:

1) Finding the "true" size of the relationship based on multiple studies.
2) Finding the average effect size based on multiple studies.
3) Finding what affects the relationship:
  - study-related (e.g. author effects, journal effects, method effects, variable selection, etc.)
  - context-related (e.g. changes over time, sample characteristics, country, etc.)
4) Uncovering publication biases (e.g. a meta-analysis of several studies with statistically significant results may conclude that there is not enough evidence)

---


```{r}

library(readxl)
metaanalysis_data <- read_excel("D:\\DSBA\\4th Semester\\Reproducible Research\\repositories\\RRcourse2023\\13. Metaanalysis\\data\\metaanalysis_data.xlsx")

```

## Case 1: Fixed Effects

```{r}
Fixed.effect <- meta::metagen(TE=Mean_boys_play_female,
             seTE=SD_boys_play_female,
             data=metaanalysis_data,
             studlab=paste(Study),
             comb.fixed = TRUE,
             comb.random = FALSE)

Fixed.effect
```
We reject null hypothesis and accept alternate hypothesis.

## Case 2: Combining both Fixed and Random Effects

```{r}
fixed.random <- meta::metacont(n.e=N_boys,
                  mean.e=Mean_boys_play_female,
                  sd.e=SD_boys_play_female,
                  n.c=N_boys,
                  mean.c=Mean_girls_play_female,
                  sd.c=SD_girls_play_female,
                  data=metaanalysis_data,
                  studlab=paste(Study),
                  comb.fixed = TRUE,
                  comb.random = TRUE,
)
fixed.random
```
The Q statistic is 129.78 with 26 degrees of freedom, and the p-value is less than 0.0001.This indicates statistically significant heterogeneity among the studies. The meta-analysis suggests a significant and negative effect based on both the common effect and random effects models. However, there is substantial heterogeneity among the included studies, indicating that the effect may vary across different contexts or populations.

## Case 3: Random Effect

```{r}
random.effect <- meta::metagen(TE=Mean_boys_play_female,
             seTE=SD_boys_play_female,
             data=metaanalysis_data,
             studlab=paste(Study),
             comb.fixed = FALSE,
             comb.random = TRUE)
random.effect
```
The Q statistic is 22.06 with 26 degrees of freedom, and the corresponding p-value is 0.6854. This p-value suggests that there is no statistically significant evidence of heterogeneity.

```{r}
Fixed.effect %>% forest(sortvar=Mean_boys_play_female)
```



```{r}
Fixed.effect %>% metareg(~ `Female authors` + `Male authors`)
  
```  


## Creating Funnel Plot


```{r}
random.effect %>% funnel()
```


```{r}
contour_levels <- c(0.70, 0.75, 0.75)
contour_colors <- c("red", "darkblue", "purple")
funnel(random.effect, contour = contour_levels, col.contour = contour_colors)
legend("topright", c("p < 0.10", "p < 0.05", "p < 0.01"), bty = "n", fill = contour_colors)
```



