---
title: "Ranczo"
author: "455395"
format: html
editor: visual
---

# Ranczo

"*Ranch*" is a Polish television comedy series, directed by [*Wojciech Adamczyk*](https://en.wikipedia.org/w/index.php?title=Wojciech_Adamczyk&action=edit&redlink=1 "Wojciech Adamczyk (page does not exist)"), that originally aired from March 25, 2006 to November 27, 2016 on [*TVP1*](https://en.wikipedia.org/wiki/TVP1 "TVP1"). It follows the story of *Lucy Wilska*, a [*Polish-American*](https://en.wikipedia.org/wiki/Polish-American "Polish-American") who has inherited her grandmother's country home in the fictional small village of *Wilkowyje*. She arrives in *Wilkowyje* with intent to sell the cottage but, after seeing the charm of the village, decides to stay. - Source: *Wikipedia*

## Picture

![Ranczo picture](https://th.bing.com/th/id/OIP.5MY6QOCiXVVQ2Y1-hkusYwHaEK?w=332&h=186&c=7&r=0&o=5&pid=1.7)

## Viewers

| Season | AVG.Viewing |
|:-------|:-----------:|
| 1      |  4 101 154  |
| 2      |  6 857 229  |
| 3      |  6 898 190  |
| 4      |  8 283 864  |
| 5      |  6 676 405  |
| 6      |  6 226 339  |
| 7      |  6 328 780  |
| 8      |  6 152 526  |
| 9      |  5 997 064  |
| 10     |   No Data   |

## View table

```{r, echo=FALSE, fig.show='asis'}
views<-c(4101154, 6857229, 6898190, 8283864, 6676405, 6226339, 6328780, 6152526, 5997064)
plot(views, type="o", col="red")
```

## Conclusion on views

```{r, include = FALSE}
x_variable <- (6857229 - 4101154)
```

Between season 1 and 2 the views increased by `r x_variable` which was the greatest change in the shows history.
