---
title: "Game of Thrones"
subtitle: "Summary Game of Thrones by Season"
author: "Nhan Nguyen"
date: today
format: 
  html:
    toc: true
    toc-depth: 2
    smooth-scroll: true
    theme:
      light: flatly
      dark: darkly
  pdf:
    lof: true
    lot: true
    pdf-engine: pdflatex
    latex-tinytex: false
number-sections: true
number-depth: 2
title-block-banner: true
execute:
  echo: fenced
params:
  season: 2  
---

```{r, echo = FALSE}
season_no <- params$season

load(paste0("../Data/season_",season_no,".RData"))

```

# Game of Thrones

#### **(*Warning:* spoilers ahead)**

------------------------------------------------------------------------

### Overview

(From the [Wikipedia](https://en.wikipedia.org/wiki/Game_of_Thrones#Premise)) Game of Thrones is an American fantasy drama television series created by David Benioff and D. B. Weiss for HBO. It is an adaptation of A Song of Ice and Fire, a series of fantasy novels by George R. R. Martin, the first of which is A Game of Thrones.

Set on the fictional continents of Westeros and Essos, Game of Thrones has a large ensemble cast and follows several story arcs throughout the course of the show. A major arc concerns the Iron Throne of the Seven Kingdoms of Westeros through a web of political conflicts among the noble families either vying to claim the throne or fighting for independence from it. Another focuses on the last descendant of the realm's deposed ruling dynasty, who has been exiled to Essos and is plotting a return to the throne. A third story arc follows the Night's Watch, a military order defending the realm against threats from the North.

------------------------------------------------------------------------

# Season summary in numbers

### Season summary

The reviewed season was:  
```{r, echo = FALSE}
start_date <- season_data$premiere_date[1]
last_epi <- max(as.numeric(season_data$no_season))
end_date <- season_data$premiere_date[last_epi]
cat(season_no)
```

Number of episodes which the season consisted of:  
```{r, echo = FALSE}
cat(last_epi)
```

The season started at:
```{r, echo = FALSE}
cat(start_date)
```

The season ended at:  
```{r, echo = FALSE}
cat(end_date)
```

The total season's viewership was:
```{r, echo = FALSE}
cat(sum(season_data$viewers))
```

The most viewed episode of the season was:
```{r, echo = FALSE, results='asis'}
max_viewers <- which.max(season_data$viewers)
name_epi <- season_data$title[max_viewers]

cat(name_epi)
```

Description of the season's most viewed episode was as follow:
```{r, echo = FALSE, results='asis'}
description <- season_data$description[max_viewers]

cat(description)
```

------------------------------------------------------------------------

You can see how the viewership of the episodes changed in Figure 1.
```{r, echo = FALSE}
#| label = "viewers_plot"
plot(season_data$viewers, type="l", col="red", lwd=5, xlab = "Episode number", ylab = "1st day TV viewers in the US (millions)")
```

------------------------------------------------------------------------

Finally, the episodes with the above-average viewership were:

| No. in season |          Title          |  Directed by   |
|:--------------|:-----------------------:|:--------------:|
| 5             | "The Wolf and the Lion" |   Brian Kirk   |
| 8             |    "The Pointy End"     | Daniel Minahan |
| 9             |        "Baelor"         |  Alan Taylor   |
| 10            |    "Fire and Blood"     |  Alan Taylor   |


------------------------------------------------------------------------

